Why do species get a thin slice of $\pi$? Revisiting Lewontin's Paradox of Variation

### 2021-05-11 manuscript/manuscript.tex
fixed tables

\documentclass[11pt]{article}
\RequirePackage{fullpage}
\RequirePackage[font=small,labelfont=bf]{caption}
\RequirePackage{amsmath,amssymb,amsthm}
\RequirePackage{mathtools}
\RequirePackage{tabularx}
\RequirePackage{graphicx}
\RequirePackage[normalem]{ulem}
\RequirePackage[hidelinks]{hyperref}
\RequirePackage{wrapfig}
\RequirePackage{subcaption}
\RequirePackage{authblk}
\RequirePackage{bm}
\RequirePackage{bbm}
\RequirePackage{tikz}
\RequirePackage{wrapfig}

@@

Notably, this relationship has few outliers and is relatively homoscedastic.
This is in part because of the log-log scale, in contrast to previous work
\parencite{Nei1984-zi,Soule1976-he}; see Supplementary Figure
\ref{suppfig:figure-1-linear} for a version on a log-linear scale. However, it
is noteworthy that few taxa have diversity estimates below $10^{-3.5}$
differences per basepair. Those that do, lynx (\emph{Lynx Lynx}), wolverine
(\emph{Gulo gulo}), and Massasauga rattlesnake (\emph{Sistrurus catenatus})
face habitat fragmentation and declining population sizes. These three species
are all in the IUCN Red List, but are listed as least concern (though their
presence in the Red List indicates they are of conservation interest). In
Supplementary Material Section \namref{supinfo:div-iucn}, I explore more about
the relationships between IUCN Red List status, diversity, and population size.

@@

\begin{table}[ht]
  \resizebox{\textwidth}{!}{%
\centering
\begin{tabular}{lr|rr|rrrr|r}
  &  & \multicolumn{2}{c}{\bf Bar-On et al.}  & \multicolumn{4}{c}{\bf Present study}  &  \\
  phylum & total species ($T$) & biomass ($B$) & prop. biomass & biomass ($b$) &  prop. biomass & num. species ($n$) &prop. total species ($f = \nicefrac{n}{T}$) & factor ($\nicefrac{b}{f B}$) \\
  \hline
  Arthropoda & $1.26 \times 10^{6}$ & 1.20 & 0.4635 & $2.77 \times 10^{-4}$ & 0.0100 &  68 & $5.41 \times 10^{-5}$ & 4.26 \\
  Chordata & $5.41 \times 10^{4}$ & 0.87 & 0.3357 & $2.68 \times 10^{-2}$ & 0.9720 &  68 & $1.26 \times 10^{-3}$ & 24.50 \\
  Annelida & $1.70 \times 10^{4}$ & 0.20 & 0.0772 & $1.24 \times 10^{-5}$ & 0.0005 &   3 & $1.76 \times 10^{-4}$ & 0.35 \\
  Mollusca & $9.54 \times 10^{4}$ & 0.20 & 0.0772 & $4.47 \times 10^{-4}$ & 0.0162 &  13 & $1.36 \times 10^{-4}$ & 16.40 \\
  Cnidaria & $1.60 \times 10^{4}$ & 0.10 & 0.0386 & $3.21 \times 10^{-5}$ & 0.0012 &   2 & $1.25 \times 10^{-4}$ & 2.57 \\
  Nematoda & $2.50 \times 10^{4}$ & 0.02 & 0.0077 & $4.00 \times 10^{-6}$ & 0.0001 &   1 & $4.00 \times 10^{-5}$ & 5.00 \\
\end{tabular}}

@@

\begin{table}[ht]
  \centering
  \begin{tabular}{rrrr}
    \hline
 & mean & 2.5 \% & 97.5 \% \\ 
 \hline
    $\beta_0$ & -2.70 & -3.00 & -2.40 \\ 
    $\beta_{LC}$ & -0.37 & -0.55 & -0.19 \\ 
    $\beta_{NT}$ & -0.19 & -0.80 & 0.41 \\ 
    $\beta_{VU}$ & -0.31 & -0.81 & 0.19 \\ 
    $\beta_{EN}$ & -0.39 & -0.71 & -0.06 \\ 
    $\beta_{CR}$ & -0.03 & -0.65 & 0.59 \\ 
    $\beta_{N_c}$ & 0.06 & 0.04 & 0.09 \\ 
    \hline
  \end{tabular}

  \caption{TODO The regression estimates of full IUCN Red List population size model
    for diversity, $\log_{10}(\pi) = \beta_0 + \beta_{LC} LC + \beta_{NT} NT +
    \beta_{VU} VU + \beta_{EN} EN + \beta_{CR} CR + \beta_{N_c} \log_{10}(N_c)$;
    $df = 165$.  Using AIC to compare this full model to a reduced model of
    $\log_{10}(\pi) = \beta_0 + \beta_{N_c} \log_{10}(N_c)$, $AIC_\text{full} =
  203.99$, $AIC_\text{reduced} =212.46$. }

\end{table}
\label{supptable:tbl-1} 
\begin{figure}[!htb]
  \centering
  \includegraphics[width=\textwidth]{figures/diversity_popsize_linear.pdf}

>>>>

\documentclass[11pt]{article}
\RequirePackage{fullpage}
\RequirePackage[font=small,labelfont=bf]{caption}
\RequirePackage{amsmath,amssymb,amsthm}
\RequirePackage{mathtools}
\RequirePackage{graphicx}
\RequirePackage[normalem]{ulem}
\RequirePackage[hidelinks]{hyperref}
\RequirePackage{wrapfig}
\RequirePackage{subcaption}
\RequirePackage{authblk}
\RequirePackage{bm}
\RequirePackage{bbm}
\RequirePackage{tikz}
\RequirePackage{wrapfig}

@@

Notably, this relationship has few outliers and is relatively homoscedastic.
This is in part because of the log-log scale, in contrast to previous work
\parencite{Nei1984-zi,Soule1976-he}; see Supplementary Figure
\ref{suppfig:figure-1-linear} for a version on a log-linear scale. However, it
is noteworthy that few taxa have diversity estimates below $10^{-3.5}$
differences per basepair. Those that do, lynx (\emph{Lynx Lynx}), wolverine
(\emph{Gulo gulo}), and Massasauga rattlesnake (\emph{Sistrurus catenatus})
face habitat fragmentation and declining population sizes. These three species
are all in the IUCN Red List, but are listed as least concern (though their
presence in the Red List indicates they are of conservation interest). In
Supplementary Material Section \Newnameref{supinfo:div-iucn}, I explore more about
the relationships between IUCN Red List status, diversity, and population size.

@@

\begin{table}[ht]
  \resizebox{\textwidth}{!}{%
\centering
\begin{tabular}{lr|rr|rrrr|r}
  &  & \multicolumn{2}{c}{\bf Bar-On et al.}  & \multicolumn{4}{c}{\bf Present study}  &  \\
  phylum & total species ($T$) & biomass ($B$) & prop. biomass & biomass ($b$) &  prop. biomass & num. species ($n$) &prop. total species ($f = \nicefrac{n}{T}$) & factor ($\nicefrac{b}{f B}$) \\
  \hline
  Arthropoda & $1.26 \times 10^{6}$ & 1.20 & 0.4635 & $2.78 \times 10^{-4}$ & 0.0100 &  68 & $5.41 \times 10^{-5}$ & 4.29 \\ 
  Chordata & $5.41 \times 10^{4}$ & 0.87 & 0.3357 & $2.70 \times 10^{-2}$ & 0.9719 &  68 & $1.26 \times 10^{-3}$ & 24.70 \\ 
  Annelida & $1.70 \times 10^{4}$ & 0.20 & 0.0772 & $1.23 \times 10^{-5}$ & 0.0004 &   3 & $1.76 \times 10^{-4}$ & 0.35 \\ 
  Mollusca & $9.54 \times 10^{4}$ & 0.20 & 0.0772 & $4.54 \times 10^{-4}$ & 0.0163 &  13 & $1.36 \times 10^{-4}$ & 16.60 \\ 
  Cnidaria & $1.60 \times 10^{4}$ & 0.10 & 0.0386 & $3.14 \times 10^{-5}$ & 0.0011 &   2 & $1.25 \times 10^{-4}$ & 2.51 \\ 
  Nematoda & $2.50 \times 10^{4}$ & 0.02 & 0.0077 & $3.89 \times 10^{-6}$ & 0.0001 &   1 & $4.00 \times 10^{-5}$ & 4.87 \\ 
\end{tabular}}

@@

\begin{table}[ht]
  \centering
  \begin{tabular}{rrrr}
    \hline
     & mean & 2.5 \% & 97.5 \% \\ 
 \hline
    $\beta_0$ & -2.80 & -3.20 & -2.50 \\ 
    $\beta_{LC}$ & -0.39 & -0.57 & -0.21 \\ 
    $\beta_{NT}$ & -0.22 & -0.83 & 0.39 \\ 
    $\beta_{VU}$ & -0.34 & -0.84 & 0.16 \\ 
    $\beta_{EN}$ & -0.40 & -0.73 & -0.07 \\ 
    $\beta_{CR}$ & -0.03 & -0.65 & 0.59 \\ 
    $\beta_{N_c}$ &  0.08 & 0.05 & 0.11 \\ 
    \hline
  \end{tabular}
  \caption{TODO The regression estimates of full IUCN Red List population size model
    for diversity, $\log_{10}(\pi) = \beta_0 + \beta_{LC} LC + \beta_{NT} NT +
    \beta_{VU} VU + \beta_{EN} EN + \beta_{CR} CR + \beta_{N_c} \log_{10}(N_c)$;
    $df = 165$.  Using AIC to compare this full model to a reduced model of
    $\log_{10}(\pi) = \beta_0 + \beta_{N_c} \log_{10}(N_c)$, $AIC_\text{full} =
  203.99$, $AIC_\text{reduced} =212.46$. }
\end{table}
\label{supptable:tbl-1}

\begin{figure}[!htb]
  \centering
  \includegraphics[width=\textwidth]{figures/diversity_popsize_linear.pdf}
